\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Stack Exchange Answers}
\author{Jesse Meng }
\date{March 5, 2018}

\begin{document}

\maketitle

\section{Original Post}
Title : strange result in calculating the expectation drawing balls from a urn with replacement

It is Question 6 on page 164 in Ross's book (Introduction to Probability Models-11th edition)

An urn contains 3 white, 6 red and 5 black balls. 6 of these balls are randomly selected from the urn with replacement. Let X and Y denote respectively the number of white and black balls selected. Compute $E[X|Y = 1]$.

Here is my steps:

Suppose Z denotes the number of red balls selected. With replacement, it follows a multinomial distribution,

$p_{X|Y}(X = 1|Y = 1)$ 

= $P(X=1,Y=1)$ / $P(Y=1)$

= $P(X = 1,Y = 1,Z = 4)$ / $P(Y = 1)$

= ${6\choose 1, 1, 4}$ $(\frac{3}{14})^1$ $(\frac{5}{14})^1$ $(\frac{6}{14})^4$ 
$/$ ${6\choose 1}$ $(\frac{5}{14})^1$ $(\frac{9}{14})^5$

= $80/243$

$p_{X|Y}(X = 2|Y = 1)$ 

= $P(X=2,Y=1)$ / $P(Y=1)$

= $P(X = 2,Y = 1,Z = 3)$ / $P(Y = 1)$

= ${6\choose 2, 1, 3}$ $(\frac{3}{14})^2$ $(\frac{5}{14})^1$ $(\frac{6}{14})^3$ 
$/$ ${6\choose 1}$ $(\frac{5}{14})^1$ $(\frac{9}{14})^5$

= $80/243$


$p_{X|Y}(X = 3|Y = 1)$ 

= $P(X=3,Y=1)$ / $P(Y=1)$

= $P(X = 3,Y = 1,Z = 2)$ / $P(Y = 1)$

= ${6\choose 3, 1, 2}$ $(\frac{3}{14})^3$ $(\frac{5}{14})^1$ $(\frac{6}{14})^2$ 
$/$ ${6\choose 1}$ $(\frac{5}{14})^1$ $(\frac{9}{14})^5$

= $40/243$

$p_{X|Y}(X = 0|Y = 1)$ 

= $P(X=0,Y = 1)$ / $P(Y=1)$

= $P(X = 0,Y = 1,Z = 5)$ / $P(Y = 1)$

= ${6\choose 0, 1, 5}$ $(\frac{3}{14})^0$ $(\frac{5}{14})^1$ $(\frac{6}{14})^5$ 
$/$ ${6\choose 1}$ $(\frac{5}{14})^1$ $(\frac{9}{14})^5$

= $32/243$

then I found 

$p_{X|Y}(X = 1|Y = 1)$ + $p_{X|Y}(X = 2|Y = 1)$ + $p_{X|Y}(X = 3|Y = 1)$ + $p_{X|Y}(X = 0|Y = 1)$


=$80/243 + 80/243 + 40/243 + 32/243$  

= $232/243$    < 1

I was stuck here. I think the above should add up to 1, but I am not sure where is wrong.

$E[X|Y]$ = $\sum_{x=0}^3 x p_{X|Y}(X|Y = 1)$



BTW, 

$E[X|Y = 1]$ can be calculated as  $5 * 3/9$ = $5/3$

Thanks in advance. Your help will be greatly appreciated.

**Update:**

Regardless of **with replacement** and **without replacement**, the expectation of $E[X|Y]$ is of the same if the number of balls selected is in a certain range.
\section{My Solution}
Your probabilities shouldn't add up to one, as you also need to consider the cases for $x=4$ and $x=5$, since $x$ should range from $0$ to $5$.
\end{document}